---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# citework

## Overview
citework is a package for creating citation networks from lists of DOI's. It has a set of function for doing the entire pipeline end-to-end. The main workhorse is `direct_citation` which does the entire shebang namely: 
1. Extracts references from the DOI's using the semantic scholar API
2. Transforms the data into a edge-list type dataframe


## Installation
This package can be installed from github using `devtools`:
```{r, message = FALSE}
devtools::install_github("Rysias/citework")
```

NB: This package doesn't use formal version control (as of yet) so you always download the "development" version
## Usage
```{r, message = FALSE}
library(citework)
library(tidyverse)
library(networkD3)
dat <- read_csv("path/to/doi_dat.csv")
# Extracts the citations
edgelist <- citework::direct_citation(dat$study_name, dat$doi)
# Plot the graph in a very simple way
network <- citework::edges_to_citework(edgelist)
network
```

## TODO
- [] Add roxygen2-style documentation to functions (Crucial)
- [] Refactor to more SOLID
- [] OPTIONAL:Change backend to tidygraph? (easier analysis)

